Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-05-21 article.tex
minor edits - included introduction start!

% What is your topic?
The topic of this paper is the environmental sustainability of vineyards within Australia.
% What is the context for your reserach?
The context of this research is that the Australian wine sector in general has gone through many tribulations due to economic, environmental and social pressures. Previously we attempted to highlight areas of concern through the use of statistical models, which were able to show strong correlations between various environmental and economic factors. However, discussions with industry and experts helped to identify that these relationships were not entirely causal, with some management and process of winegrowers obfuscating effects by directly contracting them. A key example of this was the lack of water use change during drought periods due to various methods that were used to obtain either more water or to circumvent the detrimental effects of lacking water resources.
% What do you want to achieve?
The identification of key factors; and their relation and contribution, direct or indirect, to the environmental sustainability of Australian winegrowing.
% Are there any relationships you want to explore?
This is key to this study. The relationships are in many ways more important to the research than the effects.

%%%%%%%%%%%%%%%%
% Working title
%
\title{Measuring environmental sustainability with Australian vine growers using Bayesian Networks}

@@

% Descrption
% Ensure that all readers are likely to read the nominated journal  (e.g.  few non-researchers read refereed academic journals; politicians simply don’t read).

% Notes
% Strangely this is less likely to be other researchers. Unless they are interested in Wine.

@@

@@

@@

>>>>

% What is your topic?
The topic of this paper is the environmental sustainability of vineyards within Australia.
% What is the context for your reserach?
The context of this research is that the Australian wine sector in general has gone through many tribulations due to economic, environmental and social pressures. Previously we attempted to highlight areas of concern through the use of statistical models, which were able to show strong correlations between various environmental and economic factors. However, discussions with industry and experts helped to identify that these relationships were not entirely causal, with some management and process of winegrowers obfuscating effects by directly addressing them. A key example of this was the lack of water use change during drought periods due to various methods that were used to obtain either more water or to circumvent the detrimental effects of lacking water resources.
% What do you want to achieve?
The identification of key factors; and their relation and contribution, direct or indirect, to the environmental sustainability of Australian winegrowing.
% Are there any relationships you want to explore?
This is key to this study. The relationships are in many ways more important to the research than the effects.

%%%%%%%%%%%%%%%%
% Working title
%
\title{Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards}

@@

% TODO: The original conference has fallen through we will need somewhere else.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Significance and Impact %
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Highlight the importance of this

% Stress the practical implications and potential benefits for winegrowers.

%  Explain how your research could influence policy and practice?
% TODO: How is this done in academia? The result should be measurable? yet many papers do not have impact or it would be considered "industry"? what is the noemclature of this?

@@

% TODO: I believe this is the diary industry paper.

@@

% Introduction?

% This research provides valuable insights and data that can inform and guide decisions made by policymakers and industry leaders in the Australian winegrowing sector. By identifying key sustainability factors and their interactions, this study offers evidence-based recommendations that can support the development of more effective and sustainable agricultural practices and policies.
